Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2018-09-07 paper/tidy-missing-data-paper.Rmd
* move images out of images/ folder * remove relative paths from Rmd * hopefully should compile for arxiv now

ggsave("images/geom-point-warn.png", 
       width = 4, 
       height = 4, 
       units = c("in"))

img_gg_p <- image_read("images/geom-point-warn.png")

img_gg_warn <- image_read("images/ggplot-warn.jpeg")

image_append(c(img_gg_warn, img_gg_p)) %>% 
  image_write("images/ggplot2-warning-and-plot.png", "png")

knitr::include_graphics("images/ggplot2-warning-and-plot.png")

@@

knitr::include_graphics("images/full-conversion-to-shadow.png")

@@

knitr::include_graphics("images/nabular.png")

>>>>

ggsave("geom-point-warn.png", 
       width = 4, 
       height = 4, 
       units = c("in"))

img_gg_p <- image_read("geom-point-warn.png")

img_gg_warn <- image_read("ggplot-warn.jpeg")

image_append(c(img_gg_warn, img_gg_p)) %>% 
  image_write("ggplot2-warning-and-plot.png", "png")

knitr::include_graphics("ggplot2-warning-and-plot.png")

@@

knitr::include_graphics("full-conversion-to-shadow.png")

@@

knitr::include_graphics("nabular.png")
